---
title: "IDS Final Project Proposal"
author: "Team name <br> Bobby, Nicholas, Yijing Wang, Xuze Chen and Ronan"
institute: "University of Edinburgh"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r load-packages, include = FALSE}

library(tidyverse)
library(palmerpenguins)
library(knitr)
library(xaringanthemer)


tuesdata <- tidytuesdayR::tt_load(2022, week = 32)

wheels <- tuesdata$wheels

```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r load-data, include=FALSE}
# Load your data here
```

```{r include=FALSE}
style_xaringan(
  title_slide_background_image = "img/Unknown.jpg"
)
```

#About this data frame

The data frame we have chosen is wheels.csv which is a data frame of information gathered from multiple different ferris wheels across the world.

And the question we are going to ask is how to design to most profitable ferris wheel? Along with how to make the most popular ferris wheel? And whether these are the same ferris wheels? As well as what factors caused the ferris wheels to be successful in either way?
---
## Objective

--

- Objective 1 (The first week):complete data screening, to summarize and analyze the data 

--

- Objective 2 (the second week):visualize the data across ggplot2 and anything we learned

--

- Objective 3 (the third and fourth weeks):make our hypotheses and conclusions based on the existing data and complete the presentation and write up

--

- Final objective: Display data on how to build the best Ferris wheel



---


## Data set information

- There are 21 variables including names, passengers per cabin, cost to construct, and ticket cost

--

- With the data set provided we are going to construct and compare different Ferris wheels

--
 - We are going to calculate important information to consider before starting the project
 
 --
e.g. Breakeven point, average revenue to be expected per day/month/season/year



# Example of some information you can gather from the data frame

```{r boring-analysis}
# This is the average duration of a ferris wheel ride using the variables from the data frame
ave <- round(mean(wheels$ride_duration_minutes, na.rm = TRUE))

print(ave)
```

---

# More examples of some information you can gather from the data frame

```{r recode-species, echo = FALSE}

```

```{r warning=FALSE, out.width="50%", fig.width= 6, echo=FALSE}
# Code hidden with echo = FALSE
# Uses modified iris dataset from previous chunk
# Play around with height and width until you're happy with the look
ggplot(data = wheels, mapping = aes(x = height, y = diameter, color = country)) +
  geom_point() + 
  theme_minimal() # theme options: https://ggplot2.tidyverse.org/reference/ggtheme.html
```

---

# More examples of some information you can gather from the data frame

.pull-left[
- Here is a bar graph of all the country's in the data frame and how many ferris wheels are in each of them.

- You can also see there are 73 entries with in this data frame.

]
.pull-right[
```{r warning=FALSE, out.width="200%", fig.width=6, echo=FALSE}
# see how I changed out.width and fig.width from defaults
# to make the figure bigger
ggplot(wheels, aes(x = country)) +
  geom_bar(binwidth = 2000) +
  coord_flip()

count(wheels)
```
]

---

# Heres a table of the first few entries in the data frame

```{r iris-table, echo = FALSE}
kable(head(wheels), format = "html")
```

