---
title: "IDS Final Project Proposal"
author: "Team name <br> Bobby, Nicholas, Jocelyn, Xuze Chen and Ronan"
institute: "University of Edinburgh"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r load-packages, include = FALSE}

library(tidyverse)
library(palmerpenguins)
library(knitr)
library(xaringanthemer)


tuesdata <- tidytuesdayR::tt_load(2022, week = 32)

wheels <- tuesdata$wheels

```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r load-data, include=FALSE}
# Load your data here
```

```{r include=FALSE}
style_xaringan(
  title_slide_background_image = "img/Unknown.jpg"
)
```

#About this data frame

The data frame we have chosen is wheels.csv which is a data frame of information gathered from multiple different ferris wheels across the world.

class: center, middle

## Objective

--

- Objective 1 (The first week):complete data screening, to summarize and analyze the data 

--

- Objective 2 (the second week):visualize the data across ggplot2 and anything we learned

--

- Objective 3 (the third and fourth weeks):make our hypotheses and conclusions based on the existing data and complete the presentation and write up

--

- Final objective: Display data on how to build the best Ferris wheel



---
class: inverse, center, middle
# Data set

## Data set information

- There are 21 variables including names, passengers per cabin, cost to construct, and ticket cost

--

- With the data set provided we are going to construct and compare different Ferris wheels

--
 - We are going to calculate important information to consider before starting the project
 
 --
e.g. Breakeven point, average revenue to be expected per day/month/season/year

---

# Layouts

You can use plain text

- or bullet points

.pull-left[
or text in two columns $^*$
]
.pull-right[
- like
- this
]

.footnote[
[*] And add footnotes
]

---

# Example of some information you can gather from the data frame

```{r boring-analysis}
# This is the average duration of a ferris wheel ride using the variables from the data frame
ave <- round(mean(wheels$ride_duration_minutes, na.rm = TRUE))

print(ave)
```

---

# More examples of some information you can gather from the data frame

```{r recode-species, echo = FALSE}

```

```{r warning=FALSE, out.width="50%", fig.width= 6, echo=FALSE}
# Code hidden with echo = FALSE
# Uses modified iris dataset from previous chunk
# Play around with height and width until you're happy with the look
ggplot(data = wheels, mapping = aes(x = height, y = diameter, color = country)) +
  geom_point() + 
  theme_minimal() # theme options: https://ggplot2.tidyverse.org/reference/ggtheme.html
```

---

## Plot and text

.pull-left[
- Here is a bar graph of all the country's in the data frame and how many ferris wheels are in each of them.

- You can also see there are 73 entries with in this data frame.

]
.pull-right[
```{r warning=FALSE, out.width="200%", fig.width=6, echo=FALSE}
# see how I changed out.width and fig.width from defaults
# to make the figure bigger
ggplot(wheels, aes(x = country)) +
  geom_bar(binwidth = 2000) +
  coord_flip()

count(wheels)
```
]

---

# Tables

If you want to generate a table, make sure it is in the HTML format (instead of Markdown or other formats), e.g.,

```{r iris-table, echo = FALSE}
kable(head(iris), format = "html")
```
